\Title

### 2022-09-27 Grimaldi-etal-BiolCybernetics.tex
Methods: 2.3

%
Finally, the output of the MLR model results in an event-based representation predicting at each position and time the probability for each motion. Such an output gives a form of optic flow which can be exploited for non-rigid motions, but here we defined for the sake of simplicity a readout method which applies to the full field. We have shown above that when different independent observations (here, motion estimated at different spatial locations) are known to have a common cause (here, the rigid motion of the image), then an optimal estimate of the logit of that probability is the sum of the logit of the independent probabilities. Taking the logit of the ouput probability given by the model, one can thus compute the probability for the output. This allows to compute the accuracy (as the percentage of times when the motion is exactly predicted) or the squared error $|| \speed - ||^2$ of the velocity estimate given by:
$
(u, v) = \sum_{} (u_k \cdot Pr(k \vert image) , v_k \cdot Pr(k \vert image) )
$ 
These computations are performed on a set of input which is different from that used at the training or validation stages. These metrics will be useful to compare our methods with other methods on our defined task.  The full code to reproduce the results of this paper are openly available at \url{https://github.com/SpikeAI/pyTERtorch}.  
%
\section{Results}
\label{sec:results}
%%%-----------------------------------------------------------------
%: fig:kernels
%%%-----------------------------------------------------------------
\subsection{Kernels learned for motion detection}
%%%-----------------------------------------------------------------
\begin{figure*}[ht!]
    {\centering
    %\vspace{-3cm}
    \includegraphics[width=\linewidth]{figures/motion_kernels.pdf}
    }
    %\vspace{-.5cm}
    \caption{
    	Representation of the weights for the $8$ learned kernels of the model corresponding to the OFF polarities and selective to the different motion directions
	(because of the symmetry observed between the ON and OFF event streams, kernels are similar for the ON polarities). These weights are associated to a specific delay on the \textit{delays} axis and to a presynaptic address defined on the two other axes.
	For the sake of clarity, the values in range $[-0.05, 0.05]$ are not shown. One sees positive (excitatory) coefficients for the specific direction of motion and negative (inhibitory) coefficients for all other directions.
	}
    \label{fig:kernels}
\end{figure*} 
%
%
After training our model, we first observe the weights learned for the different neurons (\seeFig{kernels}). Focusing on the positive weights, a strong selectivity is observed along specific axes for the different kernels. These directions can be easily associated to the direction of motion controlled in the motion clouds. For instance, the third and the seventh kernels show a horizontal selectivity to motion directions.
%
With the negative weights, one can observe an anti-selectivity for directions that do not correspond to the motion to which the kernel is selective to. This qualitative look at the 3D kernels allows the reader to infer for the $8$ different motion directions used to generate our synthetic event streams.

>>>>

%
Finally, the output of the MLR model results in an event-based representation predicting at each position and time the probability for each motion. Such an output gives a form of optic flow which can be exploited for non-rigid motions, but here we defined for the sake of simplicity a readout method which applies to the full field. We have shown above that when different independent observations (here, motion estimated at different spatial locations) are known to have a common cause (here, the rigid motion of the image), then an optimal estimate of the logit of that probability is the sum of the logit of the independent probabilities. Taking the logit of the ouput probability given by the model, one can thus compute the probability for the output. This allows to compute the accuracy (as the percentage of times when the motion is exactly predicted) or the squared error $|| \speed - ||^2$ of the velocity estimate given by:
$
\speed = \sum_{\class} \speed_\class \cdot Pr(\class \vert image)
$ 
These computations are performed on a set of input which is different from that used at the training or validation stages. These metrics will be useful to compare our methods with other methods on our defined task.  The full code to reproduce the results of this paper are openly available at \url{https://github.com/SpikeAI/pyTERtorch}.  
%
\section{Results}
\label{sec:results}
%%%-----------------------------------------------------------------
%: fig:kernels
%%%-----------------------------------------------------------------
\subsection{Kernels learned for motion detection}
%%%-----------------------------------------------------------------
\begin{figure*}[ht!]
    {\centering
    %\vspace{-3cm}
    \includegraphics[width=\linewidth]{figures/motion_kernels.pdf}
    }
    %\vspace{-.5cm}
    \caption{
    	Representation of the weights for the $8$ learned kernels of the model corresponding to the OFF polarities and selective to the different motion directions
	(because of the symmetry observed between the ON and OFF event streams, kernels are similar for the ON polarities). These weights are associated to a specific delay on the \textit{delays} axis and to a presynaptic address defined on the two other axes.
	For the sake of clarity, the values in range $[-0.05, 0.05]$ are not shown. One sees positive (excitatory) coefficients for the specific direction of motion and negative (inhibitory) coefficients for all other directions.
	}
    \label{fig:kernels}
\end{figure*} 
%
%
After training our model, we first observe the weights learned for the different neurons (\seeFig{kernels}). Focusing on the positive weights, a strong selectivity is observed along specific axes for the different kernels. These directions can be easily associated to the direction of motion controlled in the motion clouds. For instance, the third and the seventh kernels show a horizontal selectivity to motion directions.
%
With the negative weights, one can observe an anti-selectivity for directions that do not correspond to the motion to which the kernel is selective to. This qualitative look at the 3D kernels allows the reader to infer for the $8$ different motion directions used to generate our synthetic event streams.
